Through the eyes of the teacher

### 2021-02-08 paper_1/paper_1_supplement.Rmd
coding speaking time

The recorded lessons were coded in a post-hoc procedure with the coding software MAXQDA by previously trained raters (@kuckartz2019analyzing). The following coding scheme has been developed for coding:

``` {r coded speaking time, echo = FALSE}
### read in data for 01_01_expert_D
speaking.data.01.01 <- read.table("./data/Aperol_pilot_01_01_expert_D_cam4.txt", dec=",", sep="\t", header=T)

@@

# read in data for 01_02_expert_A
speaking.data.01.02 <- read.table("./data/Aperol_pilot_01_02_expert_A_cam1_AL", dec=",", sep="\t", header=T)

### select relevant columns
speaking.data.01.02 <- speaking.data.01.02 %>% select(
  Dokumentgruppe,
  Dokumentname,
  Code,
  Anfang,
  Ende,
  Fläche,
  Abdeckungsgrad..)

str(speaking.data.01.02)

>>>>

The recorded lessons were coded in a post-hoc procedure with the coding software MAXQDA by previously trained raters (@kuckartz2019analyzing). The following coding scheme was developed:

-

First, we coded the speaking time of the teacher and the students to compare all perspectives: coder, observer, students, teacher. The graph below shows the result of the coded speaking duration compared to the estimated speaking duration assessed with the questionnaire.

``` {r coded speaking time, echo = FALSE}
### read in data for 01_01_expert_D
speaking.data.01.01 <- read.delim("./data/Aperol_pilot_01_01_expert_D_cam4_AL_MK.txt", dec=",", sep="\t", header=T)

@@

# read in data for 01_02_expert_A
speaking.data.01.02 <- read.delim("./data/Aperol_pilot_01_02_expert_A_cam1_AL.txt", dec=",", sep="\t", header=T)

view(speaking.data.01.02)

### select relevant columns
speaking.data.01.02 <- speaking.data.01.02 %>% select(
  Dokumentname,
  Code,
  Anfang,
  Ende,
  Fläche,
  Abdeckungsgrad..)

### checking for missing values
is.na(speaking.data.01.02)
which(is.na(speaking.data.01.02))

### filter only speaking time of teacher as row 
speaking.data.01.02 <- speaking.data.01.02 %>% filter (Code == "speaking time\\teacher")

view(speaking.data.01.02)

speaking.data.01.02 <- sum(speaking.data.01.02$Abdeckungsgrad..)

# read in data for 01_03_novice_B
speaking.data.01.03 <- read.delim("./data/Aperol_pilot_01_03_novice_B_cam1.txt", dec=",", sep="\t", header=T)

view(speaking.data.01.03)

### select relevant columns
speaking.data.01.03 <- speaking.data.01.03 %>% select(
  Code,
  Anfang,
  Ende,
  Fläche,
  Abdeckungsgrad..)

str(speaking.data.01.03)

### checking for missing values
is.na(speaking.data.01.03)
which(is.na(speaking.data.01.03))

### filter only speaking time of teacher as row 
speaking.data.01.03 <- speaking.data.01.03 %>% filter (Code == "speaking time\\teachter")

speaking.data.01.03 <- sum(speaking.data.01.03$Abdeckungsgrad..)

# read in data for 01_04_novice_C
speaking.data.01.04 <- read.delim("./data/Aperol_pilot_01_04_novice_C_cam1.txt", dec=",", sep="\t", header=T)

view(speaking.data.01.04)

### select relevant columns
speaking.data.01.04 <- speaking.data.01.04 %>% select(
  Code,
  Anfang,
  Ende,
  Fläche,
  Abdeckungsgrad..)

str(speaking.data.01.04)

### checking for missing values
is.na(speaking.data.01.04)
which(is.na(speaking.data.01.04))

### filter only speaking time of teacher as row 
speaking.data.01.04 <- speaking.data.01.04 %>% filter (Code == "speaking time\\teachter")

speaking.data.01.04 <- sum(speaking.data.01.04$Abdeckungsgrad..)

# read in data for 02_01_novice_A
speaking.data.02.01 <- read.delim("./data/Aperol_pilot_02_01_novice_A_glasses.txt", dec=",", sep="\t", header=T)

view(speaking.data.02.01)

### select relevant columns
speaking.data.02.01 <- speaking.data.02.01 %>% select(
  Code,
  Anfang,
  Ende,
  Fläche,
  Abdeckungsgrad..)

str(speaking.data.02.01)

### checking for missing values
is.na(speaking.data.02.01)
which(is.na(speaking.data.02.01))

### filter only speaking time of teacher as row 
speaking.data.02.01 <- speaking.data.02.01 %>% filter (Code == "speaking time\\teacher")

speaking.data.02.01 <- sum(speaking.data.02.01$Abdeckungsgrad..)

# read in data for 02_02_novice_B
speaking.data.02.02 <- read.delim("./data/Aperol_pilot_02_02_novice_B_cam1_AL_MK.txt", dec=",", sep="\t", header=T)

view(speaking.data.02.02)

### select relevant columns
speaking.data.02.02 <- speaking.data.02.02 %>% select(
  Dokumentgruppe,
  Code,
  Anfang,
  Ende,
  Fläche,
  Abdeckungsgrad..)

str(speaking.data.02.02)

### checking for missing values
is.na(speaking.data.02.02)
which(is.na(speaking.data.02.02))

### filter only speaking time of teacher as row 
speaking.data.02.02 <- speaking.data.02.02 %>% filter (Code == "speaking time\\teacher",
                                                       Dokumentgruppe == "kodiert von Anna")

speaking.data.02.02 <- sum(speaking.data.02.02$Abdeckungsgrad..)

# read in data for 02_03_novice_C
speaking.data.02.03 <- read.delim("./data/Aperol_pilot_02_03_novice_C_cam1_AL_MK.txt", dec=",", sep="\t", header=T)

view(speaking.data.02.03)

### select relevant columns
speaking.data.02.03 <- speaking.data.02.03 %>% select(
  Dokumentgruppe,
  Code,
  Anfang,
  Ende,
  Fläche,
  Abdeckungsgrad..)

str(speaking.data.02.03)

### checking for missing values
is.na(speaking.data.02.03)
which(is.na(speaking.data.02.03))

### filter only speaking time of teacher as row 
speaking.data.02.03 <- speaking.data.02.03 %>% filter (Code == "speaking time\\teachter",
                                                       Dokumentgruppe == "02_03_kodiert von Anna")

speaking.data.02.03 <- sum(speaking.data.02.03$Abdeckungsgrad..)

# read in data for 02_04_novice_D
speaking.data.02.04 <- read.delim("./data/Aperol_pilot_02_04_novice_D_cam1.txt", dec=",", sep="\t", header=T)

view(speaking.data.02.04)

### select relevant columns
speaking.data.02.04 <- speaking.data.02.04 %>% select(
  Code,
  Anfang,
  Ende,
  Fläche,
  Abdeckungsgrad..)

str(speaking.data.02.04)

### checking for missing values
is.na(speaking.data.02.04)
which(is.na(speaking.data.02.04))

### filter only speaking time of teacher as row 
speaking.data.02.04 <- speaking.data.02.04 %>% filter (Code == "speaking time\\teachter")

speaking.data.02.04 <- sum(speaking.data.02.04$Abdeckungsgrad..)

# read in table with coded speaking time included
speaking.data <- read.delim("./data/plus_coded_speaking_time_questionnaire_data_0802.txt", dec=",", sep="\t", header=T)

# to compare both sessions filter only Identical items
speaking.data <- speaking.data  %>% filter(str_detect(scale, 
                                                 paste(c("Duration of speaking time"),
                                                    collapse = '|')))

view(speaking.data)

# value sometimes contained text before filtering, we have to convert the numbers to numeric
speaking.data <- speaking.data %>%  mutate(value = as.numeric(value))

speaking.plot <- speaking.data %>%
  ggplot(aes(x='Duration of speaking time', y=value, fill=group)) +
    geom_boxplot() +
    geom_jitter(color="black", size=0.4, alpha=0.9) +
    theme_light() +
    theme(
      legend.position="none",
      plot.title = element_text(size=11),
      axis.text.x = element_text(size = 8)) +
    facet_grid(group~perspective) +
    ggtitle("Boxplot with individual points for Duration of speaking time") +
    xlab("")
speaking.plot
